---
title: "`r sprintf('BMK Data Processing for TRI/LARI Analyses: %s', params$factor_name)`"
author: "Sirish Shrestha"
date: "2023-04-28"
params: 
  data: NULL
  factor_name: NULL
  raters: !r c("Self", "Direct Report", "Peer", "Boss")
  required_cols: NULL
  competency_item_cols: NULL
  competency_cols: NULL
  research_cols: NULL
  grouping_cols: NULL
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


```{r data-read, echo=FALSE}

df <- params$data
factor_name <- params$factor_name
raters <- params$raters
grouping_cols <- params$grouping_cols
required_cols <- params$required_cols
competency_item_cols <- params$competency_item_cols
competency_cols <- params$competency_cols
research_cols <- params$research_cols

```


Pre-process the data frame. The pre-processing steps: 

1. Group the result by `ESI_Key` and take the average of all columns by raters
2. Filter the `ESI_Key` (leaders) who have ratings from all raters `Self`, `Direct Report`, `Peer`, and `Boss`.
3. Pivot the data frame in wide format so that all raters average values are in the columns

The resulting data frame `avg_scores_by_raters_df` will be used in `lavaan` analyses.


```{r preprocess-df, echo=FALSE, warning=FALSE}

## get average item scores by rater
avg_scores_by_rater_df <- avg_scores_by_raters(df=df
                                          , required_cols=required_cols
                                          , item_cols=competency_item_cols
                                          # , competency_cols=competency_cols
                                          , research_cols=research_cols
                                          , grouping_cols=grouping_cols)


## Filter the rows for all leaders with all required raters
avg_scores_by_rater_df <- filter_rows_with_all_raters(df=avg_scores_by_rater_df
                          , id_column = "ESI_Key"
                          , raters=raters
                          , rater_colname = c("RaterType"))



## Pivot the dataframe such that raters average scores are the columns
avg_scores_by_rater_df <<- pivot_df(df=avg_scores_by_rater_df
                                 , var="RaterType"
                                 , id_column = "ESI_Key")


## set the clean dataframe as the current dataframe in the environment
set_current_df(df=avg_scores_by_rater_df)


```




