---
title: "Lavaan TRI/LARI Analyses"
author: "Sirish Shrestha"
date: "2023-04-28"
output: html_document
params: 
  data: NULL
  competency_cols: ""
  factor_name: ""
  regex_pattern: TRUE
  raters: NULL
  show_model: FALSE
  columns_for_analyses: NULL
  columns_to_remove_missing_values: NULL
  factor_weights_competency_cols: NULL
  factor_weights_cols: NULL
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


```{r assign-values, echo=FALSE}

df <- params$data
competency_cols <- params$competency_cols
factor_name <- params$factor_name
raters <- params$raters
regex_pattern <- params$regex_pattern
show_model <- params$show_model
columns_for_analyses <- params$columns_for_analyses
columns_to_remove_missing_values <- params$columns_to_remove_missing_values
factor_weights_competency_cols <- params$factor_weights_competency_cols
factor_weights_cols <- params$factor_weights_cols

```


### Perform Lavaan Analysis

There are two models to build: first level and bifactor models. Both models require the following values
 - competency_cols: Column names that make up the competency or the regex pattern to identify the columns. When providing regex pattern, `regex_pattern` value must be set to TRUE. Example: "BMK_S1_34|BMK_S1_73|BMK_S1_77"
 - factor_name: Name of the competency. This name is added in the lavaan analysis results
 - regex_pattern: Indicate whether the `competency_cols` value is regex pattern or column names
 - raters: All the raters required in the analyses

```{r first-order, echo=FALSE}

first_level <- build_first_level_model(competency_cols=competency_cols
                                       , df=df
                                       , factor_name=factor_name
                                       , raters=raters
                                       , regex_pattern = regex_pattern)

if(show_model){
  print(first_level)
}


fits <- lavaan_model_fit(df=df, model=first_level)

```



```{r bifactor,echo=FALSE}

bifactor <- build_bifactor_model(competency_cols=competency_cols
                                 , df=df
                                 , factor_name=factor_name
                                 , raters=raters
                                 , regex_pattern = regex_pattern)

bifactor_fits <- lavaan_model_fit(df=df, model=bifactor)

# bifactor_fits$orthogonal$fitted

```



```{r remove-missing-values, echo=FALSE}

df <- df %>% 
  select(matches(columns_for_analyses)) %>% 
  remove_missing_from_competency(df=.
                                , column_names=columns_to_remove_missing_values
                                , regex_pattern = TRUE)


```



```{r factory-weights, echo=FALSE}


factor_weights <- get_factor_scoring_weights(df=df
                                  , fitted_values=bifactor_fits$orthogonal$fitted
                                  , which="fsm")

## merge the factor weights with the raw item responses
df <- df %>% 
      dplyr::bind_cols(factor_weights) %>%
      as.data.frame()


df_merged <- scale_and_center_columns(df=df
                              , column_names = colnames(factor_weights)
                              , center = FALSE)

```



```{r competency-colmeans, echo=FALSE}


statistics <- compute_statistics(df=df_merged
                                 , columns = sprintf("BMK_S1_(34|73|77)(?!.*%s).*", factor_name)
                                 , regex_pattern = TRUE)


```


### Table 1

```{r statistics-table, echo=FALSE}

t_factor_weights <- t(factor_weights) %>% as.data.frame() %>% rownames_to_column(var="Item")

# Extract trait/arena names
trait_names <- unique(gsub(sprintf(".*_mean_(\\w+)_%s_.*", factor_name), "\\1", t_factor_weights$Item))

# Merge data using dplyr and tidyr
result_df <- t_factor_weights %>%
  separate(Item, into = c("Trait", "Factor"), sep = "_decisive_") %>%
  pivot_wider(names_from = "Factor", values_from = "V1") %>%
  left_join(statistics, by = c("Trait" = "Variables")) %>%
  mutate(`Mean (SD)` = sprintf("%s (%s)", Mean, SD)) %>%
  select(Item = Trait, `Mean (SD)`, Self, Direct_Report, Boss, Peer, reputation, arena) %>% 
  mutate(Self = formatC(round(Self, 3), format = "f", digits=3), 
         Direct_Report = formatC(round(Direct_Report, 3), format="f", digits=3), 
         Boss = formatC(round(Boss, 3), format="f", digits=3), 
         Peer = formatC(round(Peer, 3), format="f", digits=3), 
         reputation = formatC(round(reputation, 3), format="f", digits=3), 
         arena = formatC(round(arena, 3), format="f", digits=3))

colnames(result_df) <- c("Item", "Mean (SD)", "Self", "Direct Report", "Boss", "Peer", "Reputation", "Trait/Arena")

# 
# result_df %>% 
#   kable(caption='Table 1: Item Means, Standard Deviations, and Factor Scoring Weights Derived from the TRI/LARI Model (Normative Sample)') %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>% 
#   add_header_above(c(" " = 2, "Factor Scoring Weights" = 6)) %>%
#   footnote(general = sprintf("N = %s", format(nrow(df_merged), big.mark=", "))) 
#   

```



```{r factor-score, echo=FALSE}

factor_score_equations <- generate_factor_scores(df=df_merged
                      , competency_cols = factor_weights_competency_cols
                      , factor_weights_cols = factor_weights_cols
                      , factor_name = factor_name
                      , latent_variables=c(raters, "arena", "reputation")
                      , regex_pattern = TRUE
                      , suffix = "LV")


df_merged <- calculate_factor_scores(df=df_merged
                                     , factor_score_equations=factor_score_equations)



```



```{r correlation, echo=FALSE}

correlation <-  compute_correlation(df=df_merged
                                   , x = c(raters, "arena", "reputation")
                                   , y = bifactor_fits$orthogonal$fitted
                                   , suffix = "LV")

```


```{r performance-item, echo=FALSE}

## Create new var for performance item 1 containing the average across the three rater groups.
df_merged <- aggregate_competency_cols(df=df_merged
                                    , columns=c("BMK_S5_1_mean_Boss"
                                              , "BMK_S5_1_mean_Direct_Report"
                                              , "BMK_S5_1_mean_Peer")
                                    , aggregated_column_name="BMK_S5_1_mean_all_rater")


```



```{r compute-correlation, echo=FALSE}

correlation <- compute_correlation(df=df_merged
                             , x = c(names(factor_score_equations),
                                     "BMK_S5_1_mean_all_rater")
                             )
```





```{r conventional-average,echo=FALSE}

df_merged <- calculate_rowmeans(df=df_merged
                 , new_cols=c("Self_Avg", "Direct_Report_Avg", "Boss_Avg", 
                              "Peer_Avg", "Inf_Avg", "All_Avg")
                 , mean_cols=list(
                   c("BMK_S1_34_mean_Self", "BMK_S1_73_mean_Self", "BMK_S1_77_mean_Self"),
                   c("BMK_S1_34_mean_Direct_Report", 
                     "BMK_S1_73_mean_Direct_Report", 
                     "BMK_S1_77_mean_Direct_Report"),
                   c("BMK_S1_34_mean_Boss", "BMK_S1_73_mean_Boss", "BMK_S1_77_mean_Boss"),
                   c("BMK_S1_34_mean_Peer", "BMK_S1_73_mean_Peer", "BMK_S1_77_mean_Peer"),
                   c("BMK_S1_34_mean_Direct_Report", "BMK_S1_73_mean_Direct_Report",
                     "BMK_S1_77_mean_Direct_Report", 
                     "BMK_S1_34_mean_Boss", "BMK_S1_73_mean_Boss", "BMK_S1_77_mean_Boss", 
                     "BMK_S1_34_mean_Peer", "BMK_S1_73_mean_Peer", "BMK_S1_77_mean_Peer"),
                   c("BMK_S1_34_mean_Self", "BMK_S1_73_mean_Self", "BMK_S1_77_mean_Self", 
                     "BMK_S1_34_mean_Direct_Report", "BMK_S1_73_mean_Direct_Report",
                     "BMK_S1_77_mean_Direct_Report", "BMK_S1_34_mean_Boss", 
                     "BMK_S1_73_mean_Boss", "BMK_S1_77_mean_Boss", "BMK_S1_34_mean_Peer", 
                     "BMK_S1_73_mean_Peer", "BMK_S1_77_mean_Peer")
                   ))


```



```{r tri-lari-correlation, echo=FALSE}

correlation <- compute_correlation(df=df_merged
                                   , x = ".*_Avg|.*_LV|BMK_S5_1_mean_all_rater"
                                   , regex_pattern = TRUE
                                   )

```



```{r linear-model, echo=FALSE}

mod1 <- linear_model(formula="BMK_S5_1_mean_all_rater ~ Self_LV + Direct_Report_LV + 
                              Boss_LV + Peer_LV + reputation_LV + arena_LV"
                   , df=df_merged)

mod1$summary


mod2 <- linear_model(formula="BMK_S5_1_mean_all_rater ~ Self_Avg + Direct_Report_Avg +
                              Boss_Avg + Peer_Avg", 
                     df=df_merged)

mod2$summary

mod3 <- linear_model(formula="BMK_S5_1_mean_all_rater ~ Self_Avg + Direct_Report_Avg + 
                              Boss_Avg + Peer_Avg + Self_LV + Direct_Report_LV + Boss_LV + 
                              Peer_LV + reputation_LV + arena_LV",
                      df=df_merged)

mod3$summary


aov <- anova(mod2$model, mod3$model)
aov$summary

```

